Flowchart of Current Algorithm

### 2008-10-24 docs/flowchart/flowchart.tex
add a bit about how the (rho h)_0 edge state is computed for spherical

Here we outline the algorithm currently implemented in the code.  Our
starting point for this description are the series of papers describing
the development of the algorithm:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics}, A.~S.~Almgren, J.~B.~Bell, 
  C.~A.~Rendleman, \& M.~Zingale 2006, ApJ, 637, 922 (henceforth
  paper~I)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution} A.~S.~Almgren, J.~B.~Bell, C.~A.~Rendleman, \& M.~Zingale
  2006, ApJ, 649, 927 (henceforth paper~II)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale
  2008, ApJ, 684, 449 (henceforth paper~III)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. IV. White Dwarf Convection}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale,
  in perparation (henceforth paper~IV)
\end{itemize}

@@

@@

In paper III we discretized the enthalpy evolution equation in full, non-perturbation form.  
We have discovered that discretizing the enthalpy evolution in non-perturbational form 
leads to better numerical properties.  This is more like paper II.\\

@@

If this is the first step of the calculation ($n=0$), we set
\begin{equation}
S^{\half,\star} = \frac{S^0 + S^1}{2} \enskip ,
\end{equation}
where $S^1$ is found through the iterative process that initializes the calculation.
Otherwise, following the method used in our small-scale low Mach number algorithm
(Cite Bell04), we extrapolate to the half-time using the source
terms at the previous and current time levels
\begin{equation}
S^{\nph,\star} = S^n + \frac{\Delta t^n}{2} \frac{S^n - S^{n-1}}{\Delta t^{n-1}} \enskip .
\end{equation}

@@

>>>>

Here we outline the algorithm currently implemented in the code.  Our
starting point for this description are the series of papers describing
the development of the algorithm:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics,} A.~S.~Almgren, J.~B.~Bell, 
  C.~A.~Rendleman, \& M.~Zingale 2006, ApJ, 637, 922 (henceforth
  paper~I)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution,} A.~S.~Almgren, J.~B.~Bell, C.~A.~Rendleman, \& M.~Zingale
  2006, ApJ, 649, 927 (henceforth paper~II)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions,}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale
  2008, ApJ, 684, 449 (henceforth paper~III)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. IV. White Dwarf Convection,}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale,
  in perparation (henceforth paper~IV)
\end{itemize}
We also carry over some ideas from our small-scale low Mach number algorithm
for astrophysical flows:
\begin{itemize}
\item {\em Adaptive Low Mach Number Simulations of Nuclear Flames,}
J.~B.~Bell, M.~S.~Day, C.~A.~Rendleman, S.~E.~Woosley, \& M.~Zingale
2004, JCP, 195, 2, 677 (henceforth BDRWZ)
\end{itemize}

@@

\MarginPar{what about a $\eta_{\rho h}$}
\end{enumerate}

@@

There are several changes to the algorithm since it was last detailed
in paper III.  The major changes are:
\begin{itemize}
\item In paper III we discretized the enthalpy evolution equation in
full, non-perturbation form.  We have discovered that discretizing the
enthalpy evolution in non-perturbational form leads to better
numerical properties.  This is more like paper II.

\item We split the update of the density and enthalpy in steps 4 and 8.
Now, density is updated first, allowing us to compute new values of 
$\psi$ that are then used in the enthalpy update.

\item We discuss spherical geometries.

\item We add thermal diffusion.
\end{itemize}
%
The advance of the state through a single timestep appears as:

@@

If this is the first step of the calculation ($n=0$), we set
\begin{equation}
S^{\half,\star} = \frac{S^0 + S^1}{2} \enskip ,
\end{equation}
where $S^1$ is found through the iterative process that initializes the calculation.
Otherwise, following the method used in our small-scale low Mach number algorithm
(BDRWZ), we extrapolate to the half-time using the source
terms at the previous and current time levels
\begin{equation}
S^{\nph,\star} = S^n + \frac{\Delta t^n}{2} \frac{S^n - S^{n-1}}{\Delta t^{n-1}} \enskip .
\end{equation}

@@

   We note that for spherical geometry, the edge state of $(\rho h)_0$
   is computed by averging $h_0 \equiv (\rho h)_0/\rho_0$ and $\rho_0$
   to the edge separately, and then computing 
   ${(\rho h)_0}_{r+1/2} = {\rho_0}_{r+1/2} {h_0}_{r+1/2}$.
